\vspace*{\fill}

\vspace{1cm}
\begin{flushleft}

\large
\textbf{Acknowledgements}
% Your acknowledgement(s)    
%Who would you like to thank? 

Thanks to my supervisor Siri. First and foremost for your passion for Human-Computer Interaction and your contribution to strengthen the awareness of this field in Norway. Also, for everything you taught me during this Master's degree, and for the guidance for this thesis.  

%Secondly I want to thank my dad, for playing an important role as supporter and adviser through my whole education. Couldn't have done it without you.

I'd also like to thank my classmates, I also want to thank my classmates for helpful conversations and discussions throughout the year of master writing. 

A special thanks to my classmate, coworker and best good friend, Vilde. I'm thrilled to share this professional interest with you.  
%which I'm so proud of! Together, we are the first in Norway with this degree and are ready to conquer the future of technology.

%A special thanks to my one and only, Vilde, for holding up with me through thick and thin. Through the past two years, you have become one of my best friends, and I'm thrilled to share this professional interest with you.  
%A special thanks to coworker  my one and only, Vilde, for holding up with me through thick and thin. Through the past two years, you have become one of my best friends, and I'm thrilled to share this professional interest with you

%In memory of my beloved grandmother, Karin Saus Larsen, who always believed in me, but never saw me complete the biggest thing so far in life. 

%Thanks to the rest of my family and friends for always supporting me and bringing positive energy.  

%Last but not least, 

A big thanks to the people of Sats, for making this research possible, believing in my ideas and giving me free room to carry out the intervention. It has been exciting to get in touch with a commercial player who wants to strengthen their product and brand name. 

\vspace{1cm}

% Certification of originality
I certify that the work presented in this thesis is my own unless referenced.


% Signatures and metadata
\vspace{0.5cm}

Date: ............................
\hspace{1cm} 
City: ............................ 

\vspace{0.5cm}
Signature: ....................................................................

\vspace{0.5cm}
Total number of words: .............................................

\end{flushleft}

\vspace*{\fill}
\pagebreak